Syntax and Semantics of Abstract Binding Trees

### 2015-12-12 paper.tex
Add further motivation for sequent case study

>>>>

There are two reasons that one might want to model sequents in a (meta)-logical
framework. Perhaps the most obvious reason is to prove things about a logic
with sequent judgments; this is what motivated Crary's encoding of contexts in
LF, for instance. However, another common use-case is the practical development
of a proof assistant in which users can define new sequent rules; such
user-defined rules may only be compiled into well-behaved tactics in the proof
system in case they obey certain wellformedness properties including (among
other things) correct scoping of names. MetaPRL is a salient example of such a
proof assistant, whose implementation might have benefited from the more
principled treatment of symbols and metavariables which we present here.
